The Early Eocene Climate Optimum reconstructed with Bayesian multi-proxy integration

### 2022-08-13 manuscript/manuscript.Rmd
Update manuscript.Rmd

[Fig. 1]

## Bayesian framework
- logistic regression
- hierarchical model structure
-

[Fig. 2]
## Model validation

[Fig. 3]

- Modern data
- Sample based on Eocene localities

## Application to the EECO

@@

[Fig 1: In this part we can show a figure with the proxy data and the distributions of temperature proxies we specify, like mangroves]

## A hierarchical model of latitudinal temperature gradients ##

[Fig 2: In this part we can show a figure with the model structure and the priors we put on the parameters. Also, try it on the modern data? Alternatively, this figure goes to the SI]

- alternative to current implementation: prior on (A+DKA) instead of on DKA? Then constrain DKA to be positive by proposing it in the log-space? This would allow for putting a direct prior on the upper temperature limit

@@

## Fig 3 - Eocene gradient
## Fig 4 - compare Eocene gradient with previous reconstructions / ES models

>>>>

[Fig 1: Map and distribution of proxy data and ecological data]

## Bayesian framework
- logistic regression
- hierarchical model structure
- choice of priors (based on modern, see below)

[Fig. 2: Model structure and visualisation of parameters and priors]

## Model validation

[Fig. 3]
- Modern data
- Sample based on Eocene localities

## Model application
- Calculate lat gradient
- Calculate global T

@@

@@

## Model validation
- Show that the modern gradient can be reproduced with Eocene sampling distribution
[Fig 3 - Modern gradient]

## EECO reconstruction
- Show Eocene gradient 
- Global t
- report lat gradient

## Fig 4 - compare Eocene gradient with previous reconstructions / ES models
